HTW E1 Testing

### 2023-08-26 Analysis/Appendix/E1_Appendix.qmd
alt. slope models

>>>>

```{r}
#| label: fig-e1-ame
#| fig-cap: E1. Predicted Means Per Condition and Band, and Average Marginal Effect (Constant - Varied)
#| fig-width: 10
#| fig-height: 10

new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")])))

cSamp <- e1_distBMM  |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
          epred = TRUE, re_formula = NA) |> 
  pairs() |> gather_emmeans_draws()  |>
  group_by(contrast, .draw,bandInt) |> summarise(value=mean(.value), n=n())

 ameBand <- cSamp |> ggplot(aes(x=value,y="")) + 
  stat_halfeye() + 
  geom_vline(xintercept=0,alpha=.4)+
  facet_wrap(~bandInt,ncol=1) + labs(x="Marginal Effect (Constant - Varied)", y= NULL)+
  ggtitle("Average Marginal Effect")

bothConditGM <- e1_distBMM %>%
  epred_draws(newdata = new_data_grid,ndraws = 2000, re_formula = NA) |>
  ggplot(aes(x=.epred,y="Mean",fill=condit)) + 
  stat_halfeye() +facet_wrap(~bandInt, ncol = 1) +
  labs(x="Predicted Deviation", y=NULL)+
  ggtitle("Grand Means") +theme(legend.position = "bottom")

(bothConditGM | ameBand) + plot_layout(widths=c(2,1.0))
```

### 2023-08-26 Analysis/e1_test.qmd
alt. slope models

::: {layout-ncol=2}

@@

```{r}
#| label: tbl-e1-bmm-dist
#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"

@@

@@

:::

@@

```{r}
#| label: fig-e1-ame
#| fig-cap: E1. Predicted Means Per Condition and Band, and Average Marginal Effect (Constant - Varied)
#| fig-width: 10
#| fig-height: 10
new_data_grid=map_dfr(1, ~data.frame(unique(test[,c("id","condit","bandInt")])))

cSamp <- e1_distBMM |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
          epred = TRUE, re_formula = NA) |> 
  pairs() |> gather_emmeans_draws()  |>
  group_by(contrast, .draw,bandInt) |> summarise(value=mean(.value), n=n())

 ameBand <- cSamp |> ggplot(aes(x=value,y="")) + 
  stat_halfeye() + 
  geom_vline(xintercept=0,alpha=.4)+
  facet_wrap(~bandInt,ncol=1) + labs(x="Marginal Effect (Constant - Varied)", y= NULL)+
  ggtitle("Average Marginal Effect")

bothConditGM <- e1_distBMM %>%
  epred_draws(newdata = new_data_grid,ndraws = 2000, re_formula = NA) |>
  ggplot(aes(x=.epred,y="Mean",fill=condit)) + 
  stat_halfeye() +facet_wrap(~bandInt, ncol = 1) +
  labs(x="Predicted Deviation", y=NULL)+
  ggtitle("Grand Means") +theme(legend.position = "bottom")

(bothConditGM | ameBand) + plot_layout(widths=c(2,1.0))
```

#### Discrimination between Velocity Bands

In addition to accuracy/deviation. We also assessed the ability of participants to reliably discriminate between the velocity bands (i.e. responding differently when prompted for band 600-800 than when prompted for band 150-350). @tbl-e1-test-nf-vx shows descriptive statistics of this measure, and Figure 1 visualizes the full distributions of throws for each combination of condition and velocity band. To quantify discrimination, we again fit Bayesian Mixed Models as above, but this time the dependent variable was the raw x velocity generated by participants on each testing trial.

\begin{equation}
vx_{ij} = \beta_0 + \beta_1 \cdot condit_{ij} + \beta_2 \cdot bandInt_{ij} + \beta_3 \cdot condit_{ij} \cdot bandInt_{ij} + b_{0i} + b_{1i} \cdot bandInt_{ij} + \epsilon_{ij}
\end{equation}

@@

See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition (β = 146, 95% CI [35.96, 254.70]) suggests that the varied group tends to produce harder throws than the constant group. Most relevant to the issue of discrimination is the slope on Velocity Band (β = 0.69, 95% CI [.59, .77]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The slope coefficient (β = 0.69 ) also seems in accordance with an examination of @tbl-e1-test-nf-vx, which shows that average x-velocity fell within the range of the target band for four out of six of the bands ($4/6$=.67). The estimate for the interaction between slope and condition (β = -.12, 95% CI [-.25, 0.00]), suggests that the varied condition had significantly lower slopes than did the constant group. This difference is depicted visually in @fig-e1-bmm-vx.

@@

>>>>

@@

```{r}
#| label: tbl-e1-bmm-dist
#| tbl-cap: "Experiment 1. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
#| tbl-subcap: ["Model Coefficients", "Contrasts"]
#| layout-ncol: 2
#| echo: fenced
#| column: page-inset-right

@@

e1_distBMM |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
          epred = TRUE, re_formula = NA) |> 
  pairs() |> gather_emmeans_draws()  |> 
   summarize(median_qi(.value),pd=sum(.value>0)/n()) |>
   select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
   mutate(across(where(is.numeric), \(x) round(x, 2)),
          pd=ifelse(value<0,1-pd,pd)) |>
   kbl()

@@

@@

#### Discrimination between bands

@@

See @tbl-e1-bmm-vx for the full model results. The estimated coefficient for training condition (β = 164.67, 95% CrI [45.50, 278.85]) suggests that the varied group tends to produce harder throws than the constant group, but is not in and of itself useful for assessing discrimination. Most relevant to the issue of discrimination is the slope on Velocity Band (β = 0.71, 95% CrI [.62, .80]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibited some discrimination between bands. The slope coefficient (β = 0.71 ) also seems in accordance with an examination of @tbl-e1-test-nf-vx, which shows that average x-velocity fell within the range of the target band for four out of six of the bands ($4/6$=.67). The estimate for the interaction between slope and condition (β = -.12, 95% CI [-.25, 0.00]), suggests that the varied condition had significantly lower slopes than did the constant group. This difference is depicted visually in @fig-e1-bmm-vx.

```{r}
#| label: tbl-vx-emmeans
#| tbl-cap: Conditional Means and Contrasts
#| tbl-subcap: ["6 Band Model Contrasts", "3 Band Model Contrasts"]
#| layout-ncol: 2
#| echo: fenced
#| column: page-inset-right

e1_vxBMM  |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
          epred = TRUE, re_formula = NA) |> 
  pairs() |> 
  gather_emmeans_draws()  |> 
  summarize(pd=sum(.value>0)/n(), median_hdi(.value) ) |> 
  select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
  mutate(pd=ifelse(value<0,1-pd,pd),across(where(is.numeric), \(x) round(x, 2))) |>
  kbl()

e1_extrap_VxBMM |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600)),
          epred = TRUE, re_formula = NA) |> 
  pairs() |> 
  gather_emmeans_draws()  |> 
  summarize(pd=sum(.value>0)/n(), median_hdi(.value) ) |> 
  select(contrast,Band=bandInt,value=y,lower=ymin,upper=ymax,pd) |> 
  mutate(pd=ifelse(value<0,1-pd,pd),across(where(is.numeric), \(x) round(x, 2))) |>
  kbl()

@@

 ggplot(indvSlopes, aes(x = Slope, color = condit)) + 
  geom_density()
